A Model for Extracting Time Delays from Noisy Time Series Data

### 2013-08-14 doc/Paper1/ms.tex
Slight fix

The sampling distributions (and hence the likelihood function) will then be
written as a probability distribution for the measurements $\boldsymbol{D}$
given the time delay $\tau$ along with some nuisance parameters.

>>>>

The sampling distributions (and hence the likelihood function) will then be
written as a probability distribution for the measurements $\boldsymbol{D}$
given the time delay $\tau_2$ along with some nuisance parameters.

\section{Sampling Distribution}
